Proof Reconstruction with Athena\\(Work in Progress)

### 2017-04-21 slides/slides.tex
[ slides ] playing with fonts.

\documentclass[hyperref={pdfpagelabels=false}]{beamer}
\beamertemplatenavigationsymbolsempty
\usepackage[utf8x]{inputenc}
\usepackage{amsmath, amsthm, amssymb}
%\usepackage{bm}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{lmodern}
\usepackage{url}
\usepackage[T1]{fontenc}

\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}

\lstset{
    aboveskip=10pt
  , backgroundcolor=\color{aliceblue}
  , basicstyle=\ttfamily
  , belowskip=9pt
  , frame=trbl
  , keywords=[2]{axiom, conjecture,inference, negated_conjecture, plain}
  , keywords=[3]{fof, cnf}
  , keywords=[4]{canonicalize, resolve, conjunct, strip, simplify, negate, clausify}
  , keywordstyle=[2]\color{cadet}%\underbar,%\bfseries
  , keywordstyle=[3]\color{bondiblue}\bfseries
  , keywordstyle=[4]\bfseries
  , showstringspaces=false
}

\newcommand{\problemtptp}[3][c]{\lstinputlisting[caption=#2, firstline=#3, label=custom#1]{#2}}
\newcommand{\solutiontstp}[2][c]{\lstinputlisting[caption=#2, firstline=5, label=custom#1]{#2}}

\title{Proof Reconstruction with Athena\\(Work in Progress)}

\date{Agda Implementors’ Meeting XXV}

\author{Jonathan Prieto-Cubides}

>>>>

\documentclass[xetex, mathserif, serif,hyperref={pdfpagelabels=false}]{beamer}

% --------------------------------------------------------------------------
% Color definitions.
% --------------------------------------------------------------------------
\usepackage{xcolor}
\definecolor{amethyst}{rgb}{0.6, 0.4, 0.8}
\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
\definecolor{blue(munsell)}{rgb}{0.0, 0.5, 0.69}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{blu}{RGB}{1,0,102}
\definecolor{brightmaroon}{rgb}{0.76, 0.13, 0.28}
\definecolor{bondiblue}{rgb}{0.0, 0.58, 0.71}
\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
\definecolor{ashgrey}{rgb}{0.7, 0.75, 0.71}
\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}
% --------------------------------------------------------------------------

% --------------------------------------------------------------------------
% Beamer configuration.
% --------------------------------------------------------------------------
\usetheme{default}
\usecolortheme{default}
\beamertemplatenavigationsymbolsempty
\hypersetup{pdfpagemode=UseNone}

\setbeamertemplate{footline}{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.8\paperwidth,ht=2.25ex,dp=1ex,left]{headFoot}%
    \hspace*{2ex}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.2\paperwidth,ht=2.25ex,dp=1ex,right]{headFoot}%
    \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
  \end{beamercolorbox}}%
  \vskip0pt%
}

\setbeamercolor{headFoot}{fg=gray,bg=aliceblue}
\setbeamercolor{institute}{fg=blu}
\setbeamercolor{normal text}{fg=blu}
\setbeamercolor{subtitle}{fg=blu}
\setbeamercolor{titlelike}{fg=blu}
\setbeamerfont{footnote}{size=\tiny}
\setbeamercolor{block title}{bg=blue,fg=blu}
\setbeamercolor{block body}{bg=aliceblue}
\setbeamercolor{item}{fg=blu} % color of bullets
\setbeamercolor{subitem}{fg=blu}
\setbeamercolor{itemize/enumerate subbody}{fg=blu}
\setbeamertemplate{itemize subitem}{{\textendash}}
\setbeamerfont{itemize/enumerate subbody}{size=\footnotesize}
\setbeamerfont{itemize/enumerate subitem}{size=\footnotesize}
% --------------------------------------------------------------------------

\usepackage[english]{babel}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{bussproofs}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage{url}
\usepackage{lstagda}

\usefonttheme{professionalfonts}
\usefonttheme{serif}
\usepackage{fontspec}
\setmainfont[ExternalLocation=fonts/
  , BoldFont=Vollkorn-Bold.ttf
  , ItalicFont=Vollkorn-Italic.ttf
  , BoldItalicFont=Vollkorn-BoldItalic.ttf
  ]{Vollkorn-Regular.ttf}

\usepackage{mathtools}
\usepackage{unicode-math}

%\setmainfont{xits-regular.otf}
\setmathfont{xits-mathbold.otf}

\newfontfamily\SourceCode{SourceCodePro-Semibold.ttf}
\newfontfamily\SourceCodeIt{SourceCodePro-It.ttf}
\setmonofont{SourceCodePro-Semibold.ttf}

\newcommand{\problemtptp}[3][c]{\lstinputlisting[style=tptp,caption=#2, firstline=#3, label=custom#1]{#2}}
\newcommand{\solutiontstp}[2][c]{\lstinputlisting[style=tptp,caption=#2, firstline=5, label=custom#1]{#2}}

\title{Proof Reconstruction with Athena\\(Work in Progress)}
\date{Agda Implementors’ Meeting XXV}
\author{Jonathan Prieto-Cubides}
